Estimating Gaze Duration Error from Eye Tracking Data

### 2023-03-01 paper/paper.tex
Uncommited paper changes

\subsection{Experiments}

We apply the \textit{gazerr} application to investigate the relationship between 
measured gaze duration and expected true duration under a variety of changing scenarios. 
These scenarios are variations in the underlying error indicated by the eye tracking 
calibration file and length of the session in which the user could be looking at 
the area of interest.

@@

We include these biased calibration dataset as they are consistent with both our 
observations of real eye tracking data and what is found in the literature\cite{}.
We use this synthetic data creation in order to explore the extent to which different
patterns in error, bias and precision affects gaze duration measurements.

@@

\begin{figure}[h!]
\includegraphics[scale=0.5]{../results/Measured_vs_expected.png}
\caption{Measured Versus Expected Gaze Duration. \\\hspace{\textwidth} 
MREC ad appearing on screen for 1s with 50px Mean Error in Fixation}
\label{fig:measured_vs_expected}
\end{figure}

The result shown in Figure \ref{fig:measured_vs_expected} is indicative of what we see under
multiple variations of the simulation configuration. At lower meaurement values there is a 
tendency for the measurement to be an accurate estimation of true gaze duraiton, while 
at higher values it tends toward an under-estimation of the true gaze duration. 
Surprisingly the results using the biased calibration data seem to mitigate this effect 
somewhat, but the overall pattern remains consistent.

@@

In our final experiment we look at the effect of both the size of the measured 
gaze duration and the mean error of fixation on the expected error in gaze duration.
We display this as a three dimensional expected error surface over these two key dimensions
in Figure \ref{fig:error_surface}

@@

We have released this approach as the open source application \textit{gazerr} and used it to explore
the relationship between fixation error and duration error. Our results show that the nature
of the error in gaze duration depends on the size of the measurement. Smaller measurements
tend to have lower expected error while larger measurements tend toward under prediction. We plotted
the relationship between expected error and saw that observed tendency toward smaller duration
measurements (estimated with an psuedo-exponential distribution) delivers a slower growing
expected duration error with the mean error in fixation points.

Finally, our simulations revealed that for large error in fixation points, certain measurements
become so unlikely that our Monte Carlo simualtions placed none of the probability density
in those regions. This strongly suggests that an additional downside to large fixation point error
is a reduced range of measurement for area of interest studies.

>>>>

\section{Experiments}

We apply the \textit{gazerr} application to investigate the relationship between 
measured gaze duration and expected true duration under a variety of scenarios. 
Each scenario involves a variation in the underlying error indicated by the eye tracking 
calibration file and length of the session in which the user could be looking at 
the area of interest.

@@

We include these biased calibration datasets as they are consistent with both our 
observations of real eye tracking data and what is found in the literature\cite{}.
We use this synthetic data creation in order to explore the extent to which different
patterns in error, bias and precision affects gaze duration measurements.

@@

\begin{figure}[h!]
\includegraphics[scale=0.5]{../results/Measured_vs_expected.png}
\caption{Measured Gaze Duration Versus Expected Gaze Duration. \\\hspace{\textwidth} 
MREC ad appearing on screen for 1s with 70px Mean Error in Fixation}
\label{fig:measured_vs_expected}
\end{figure}

The result shown in Figure \ref{fig:measured_vs_expected} is indicative of what we 
see under multiple variations of the simulation configuration. 
At lower meaurement values there is a tendency for the measurement to be an 
accurate estimation of true gaze duration, while 
at higher values it tends toward an under-estimation of the true gaze duration.
This problem is worse for the model with the biased error, but it is mitigated
when the biased error comes from a model with higher precision. This is potentially
due to the fact that the high prescion scenario has lower tendency for gaze to be 
pushed off screen.

@@

In addition, the additional error in gaze duration we see when the error is biased
in a particular direction (shown in B) is partly mitigated by a fixation model that
is more precise (shown in C). This suggests that a precise fixation sampling process
is able to partly overcome the false positive and false negatives of an error prone gaze
fixation model.

In our final experiment we look at the effect of both the size of the measured 
gaze duration and the mean error of fixation on the expected error in gaze duration.
We conduct this experiment using only the unbiased synthetic data in order to understand
how error centred on true fixation points relates to error in gaze duration across the
range of measurement. We display these results as a three dimensional expected error 
surface over these two key dimensions in Figure \ref{fig:error_surface}

@@

We have released this approach as the open source application \textit{gazerr} and 
used it to explore the relationship between fixation error and duration error, under
range of realistic error profiles when looking at measuring attention on a standard
size ad within a mobile screen. Our results show that the nature
of the error in gaze duration tends to depend on the size of the measurement. 
Smaller measurements tend to have lower expected error while larger measurements 
tend toward under prediction. 
We plotted the relationship between expected error and saw that the observed 
tendency toward smaller duration measurements 
(estimated with an psuedo-exponential distribution) delivers a slower growing
expected duration error with the mean error in fixation points.

Finally, our simulations revealed that for large error in fixation points, 
certain measurements become so unlikely that our Monte Carlo simulations placed 
none of the probability density in those regions. 
This strongly suggests that an additional downside to large fixation point error
is a reduced range of measurement for area of interest studies.
